---
title: "Bayesian Change-Point Analysis of Texas Summer Temperatures"
subtitle: "STAT 638 Project 9 - Austin Camp Mabry, TX (1938-2026)"
author: "Campbell Brickhouse, Shandon Bringhurst, Caleb Notheis"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(dplyr)
library(ggplot2)
source(here("R", "clean_data.R"))
source(here("R", "annual_summary.R"))

clean  <- readr::read_csv(here("data", "processed", "data_cleaned.csv"), show_col_types = FALSE)
annual <- compute_annual_summer_tmax(clean)
```

## Scientific Question and Data

- Has average summer (Jun-Aug) daily max temperature at Austin Camp Mabry, TX changed over time?
- Gradual trend vs. one or more abrupt change points?
- Data: NOAA GHCN-D daily TMAX, station USW00013958, `r min(annual$year)`-`r max(annual$year)`
- Outcome $Y(t)$: mean daily TMAX over Jun 1 - Aug 31 of year $t$, years with $\geq$ 90% of summer days present

## Bayesian Model

- *(state the likelihood for $Y(t)$ and how segment-specific means/slopes and change-point location(s) enter the model)*

## Prior Distributions

- *(state and justify priors for the mean/slope parameters and the change-point location)*

## Posterior Computation and Diagnostics

- *(MCMC method, chains/iterations, $\hat{R}$, effective sample size, trace plots)*

## Bayesian Results

```{r annual-trend-plot}
ggplot(filter(annual, included), aes(year, mean_tmax_f)) +
  geom_point() +
  geom_smooth(method = "loess", se = TRUE) +
  labs(x = "Year", y = "Mean summer TMAX (deg F)")
```

## Bayesian Results / Interpretation

- *(posterior summary of change-point location and magnitude, credible intervals)*

## Sensitivity Analysis and Model Checking

- *(alternative priors / posterior predictive checks; are conclusions robust?)*

## Alternative Analysis and Bayesian Comparison

- *(frequentist change-point or trend test; how do estimates/uncertainty compare?)*

## Innovation / Extension

- Motivation $\rightarrow$ Extension $\rightarrow$ What we learned

## Conclusions and Justification for the Bayesian Approach

- Answer to the scientific question
- Did the Bayesian approach offer a meaningful advantage over the alternative?
