---
title: "Bayesian Change-Point Analysis of Texas Summer Temperatures"
author: "Campbell Brickhouse, Shandon Bringhurst, Caleb Notheis"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

<!--
Section word-count targets are from instructions.md. The main report is
capped at 2,500 words excluding references, captions, supplementary
material, and the AI Use Statement. Keep routine code collapsed (code_folding
above) or move it to the Appendix so it doesn't count against the limit.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(here)
library(dplyr)
library(ggplot2)
source(here("R", "clean_data.R"))
source(here("R", "annual_summary.R"))

clean  <- readr::read_csv(here("data", "processed", "data_cleaned.csv"), show_col_types = FALSE)
annual <- compute_annual_summer_tmax(clean)
```

## 1. Scientific Question and Data (200-250 words)

*State the scientific question, data source, outcome, key predictors, sample size, and relevant features.*

```{r data-overview}
annual |>
  summarise(
    n_years = n(),
    n_included = sum(included),
    first_year = min(year),
    last_year = max(year)
  )
```

## 2. Bayesian Model (250-300 words)

*Specify the likelihood, parameters, and why the model fits the scientific question.*

## 3. Prior Distributions (250-300 words)

*Specify and justify priors; state whether informative, weakly informative, or otherwise motivated.*

## 4. Posterior Computation and Diagnostics (250-300 words)

*Describe the posterior computation method and convergence/computational diagnostics.*

## 5. Posterior Results and Interpretation (350-400 words)

*Present posterior means/medians, credible intervals, posterior probabilities, or predictions, interpreted for the scientific question.*

## 6. Sensitivity Analysis and Model Checking (250-300 words)

*At least one sensitivity analysis on priors or modeling assumptions; posterior predictive or other model checks.*

## 7. Alternative Analysis, Comparison, and Bayesian Justification (400-450 words)

*Frequentist or other established alternative method; compare estimates, uncertainty, assumptions, predictions, interpretation, conclusions.*

## 8. Innovation or Extension (200-250 words)

*Motivation, extension, what was learned. Explicitly answer: why is the Bayesian approach justified here, and what does it provide beyond the alternative?*

## AI Use Statement (max 50 words)

*Which AI tools were used, how, and how the group verified AI-generated statistical/computational information.*

## References

## Appendix: Full Analysis Code
